---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, error = FALSE)
```

# Stratified Sampling for Survey Site Selection

## Random Sampling *Without* Prior Stratification

Random sampling without prior stratification may produce a sample with imbalances of key features. Here data on 314 sites, which have 4 features of interest:

```{r}
library(tidyverse)
library(janitor)
library(gt)

dat <- read_csv("./data/dummy_data_survey_sample.csv")

dat %>%
  gt_preview()


```

If a small sample must be taken (for example, due to prohibitive study costs), a random sampling process can still leave unbalanced features. Here are the features in the whole population:

```{r}

dat %>%
  summarise_at(.vars = vars(feature1, feature2, feature3, feature4), .funs = ~ sum(.x)/length(.x)) %>%
  gt() %>%
  gt::fmt_percent(columns = everything()) %>%
  gt::tab_header(title = gt::md("Percent of *Total* with Feature Detected"))


```

Here are the features in the small random sample:

```{r}

set.seed(18)

dat %>%
  slice_sample(n = 14) %>%
  summarise_at(.vars = vars(feature1, feature2, feature3, feature4), .funs = ~ sum(.x)/length(.x)) %>%
  gt() %>%
  gt::fmt_percent(columns = everything()) %>%
  gt::tab_header(title = md("Percent of *Sample* with Feature Detected"))


```

## Random Sampling *With* Prior Stratification

Stratified sampling ensures better balance of key features:

```{r}

set.seed(18)

dat %>%
  group_by(feature1, feature2, feature3, feature4) %>%
  # note: 16 groups total, based on this feature distribution
  slice_sample(n = 1) %>%
  ungroup() %>%
  slice_sample(n = 14) %>%
  summarise_at(.vars = vars(feature1, feature2, feature3, feature4), .funs = ~ sum(.x)/length(.x)) %>%
  gt() %>%
  gt::fmt_percent(columns = everything()) %>%
  gt::tab_header(title = md("Percent of *Stratified Sample* with Feature Detected"))


```




